\documentclass[]{interact}

% ==========================================
% 1. DRAFTING TOOLS (WATERMARKS & TODOS)
% ==========================================
% Toggle this to 'true' while writing to see todos and watermarks.
% MUST BE SET TO 'false' FOR FINAL SUBMISSION.
\newif\ifdraftversion
\draftversionfalse 

\ifdraftversion
  \usepackage{draftwatermark}
  \SetWatermarkText{DRAFT}
  \SetWatermarkScale{0.8}
  \SetWatermarkColor[gray]{0.95}
  \usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
\else
  \usepackage[disable]{todonotes}
\fi

% ==========================================
% 2. ENCODING & TYPOGRAPHY
% ==========================================
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel} 
\usepackage{csquotes}
\usepackage{microtype} % Still safe to use; prevents overfull hboxes

% ==========================================
% 3. ADVANCED TABLES & FIGURES
% ==========================================
% interact.cls natively loads: graphicx, booktabs, rotating. Do not reload them.

% T&F specific subfigure package (Do NOT use subcaption here)
\usepackage[caption=false]{subfig} 

% Smart table tools
\usepackage{multirow} 
\usepackage{makecell} 
\usepackage{siunitx}  
\sisetup{detect-all, group-separator={,}} 

% TikZ & PGFPlots (For vector diagrams)
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

% ==========================================
% 4. COLORS & CODE LISTINGS
% ==========================================
\usepackage{xcolor}
\definecolor{codebg}{RGB}{245, 245, 245}
\definecolor{codecomment}{RGB}{92, 99, 112}
\definecolor{codekeyword}{RGB}{30, 64, 175}
\definecolor{codestring}{RGB}{14, 116, 144}

\usepackage{listings}
\lstdefinestyle{customcode}{
    basicstyle=\ttfamily\small,
    keywordstyle=\color{codekeyword}\bfseries,
    commentstyle=\color{codecomment}\itshape,
    stringstyle=\color{codestring},
    backgroundcolor=\color{codebg},
    showstringspaces=false,
    inputencoding=utf8,
    breaklines=true,
    frame=single,
    framerule=0.4pt,
    rulecolor=\color{black!20},
    xleftmargin=0.4em,
    xrightmargin=0.4em,
    aboveskip=0.8em,
    belowskip=0.8em,
    numbers=left,
    numberstyle=\tiny\color{codecomment}
}
\lstset{style=customcode}

% ==========================================
% 5. MATHEMATICS & THEOREMS
% ==========================================
% interact.cls natively loads amsmath, amssymb, amsthm.
% These are the exact theorem setups required by T&F:
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

% ==========================================
% 6. BIBLIOGRAPHY (T&F APA Style)
% ==========================================
% T&F uses natbib for this specific template layout
\usepackage[longnamesfirst,sort]{natbib}
\bibpunct[, ]{(}{)}{;}{a}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}

% ==========================================
% 7. HYPERLINKS & CROSS-REFERENCES
% ==========================================
% Note: Always load hyperref near the end, and cleveref last.
\usepackage[
  colorlinks=true, 
  linkcolor=blue!40!black, 
  urlcolor=blue!40!black, 
  citecolor=blue!40!black
]{hyperref}

\usepackage[nameinlink,noabbrev]{cleveref} 

\newcommand{\linkurl}[1]{\href{#1}{\textcolor{blue}{\underline{\small\nolinkurl{#1}}}}}

% ==========================================
% DOCUMENT START
% ==========================================
\begin{document}

% Optional: Specify article type (e.g., RESEARCH ARTICLE, REVIEW)
\articletype{RESEARCH ARTICLE} 

\title{Your Brilliant Journal Title Goes Here}

\author{
\name{First Author\textsuperscript{a}\thanks{CONTACT First Author. Email: author@university.edu} and Second Author\textsuperscript{b}}
\affil{\textsuperscript{a}Department of Science, University of Examples, City, Country; \textsuperscript{b}Department of Research, Institute of Technology, City, Country}
}

\maketitle

% ==========================================
% ABSTRACT & KEYWORDS
% ==========================================
\begin{abstract}
This is the abstract of your paper. Keep it concise and ensure it directly summarizes your research question, methodology, and primary findings. The \texttt{interact} class formats this automatically to T\&F standards.
\end{abstract}

\begin{keywords}
Keyword one; keyword two; keyword three; formatting; submission
\end{keywords}

% Print To-Dos if in drafting mode
\ifdraftversion
  \listoftodos
  \clearpage
\fi

% ==========================================
% MAIN CONTENT
% ==========================================
\section{Introduction}
Start your manuscript here. You can safely use your custom tools, such as \todo{Write the literature review} leaving to-do notes for yourself. 

When referencing standard figures, use \cref{fig:example} to automatically generate the word "Figure". For citations, because this template uses \texttt{natbib} APA style, use \verb|\citep{Smith2023}| for parenthetical citations like \citep{Smith2023}, and \verb|\citet{Smith2023}| for narrative citations like \citet{Smith2023}.

\section{Methodology}
\subsection{Advanced Formatting}

Here is an example of a T\&F compliant table using your \texttt{booktabs} upgrade:

\begin{table}[ht]
\tbl{Example of a perfectly formatted scientific table.}
{\begin{tabular}{l c c} \toprule
  Metric & Group A & Group B \\ \midrule
  Velocity (\unit{\meter\per\second}) & 12.4 & 15.2 \\
  Accuracy (\%) & 98.1 & 94.3 \\ \bottomrule
\end{tabular}}
\label{tab:results}
\end{table}

\section{Conclusion}
Wrap up your paper here. All of your structural styling, fonts, and layouts are safely offloaded to the \texttt{interact} class, ensuring you will have zero typesetting conflicts when submitting to the ScholarOne/Editorial Manager system.

% ==========================================
% BACKMATTER
% ==========================================
\section*{Disclosure statement}
No potential conflict of interest was reported by the author(s).

\section*{Funding}
This work was supported by the [Grant Agency] under Grant [number xxxx].

% ==========================================
% REFERENCES
% ==========================================
% Ensure your references.bib file is in the same directory.
\bibliographystyle{apacite} % Or whichever specific BST file T&F asks for
\bibliography{references}

\end{document}
